### i want you to write some r code to carry out rotations in 3d space

Rotating objects in 3D space involves using rotation matrices. These matrices are used to transform the coordinates of points in 3D space to achieve the effect of rotation around the X, Y, or Z axis.

Below is an example of R code that defines functions to create rotation matrices for each axis and a function to apply these rotations to a set of 3D points. This code uses base R functionalities, hence no additional libraries are required.

```{r}
# Function to create a rotation matrix for rotation around the X-axis
rotation_matrix_x <- function(angle_degrees) {
  angle_radians <- angle_degrees * (pi / 180)
  matrix(c(1, 0, 0,
           0, cos(angle_radians), -sin(angle_radians),
           0, sin(angle_radians), cos(angle_radians)), 
         ncol = 3, byrow = TRUE)
}

# Function to create a rotation matrix for rotation around the Y-axis
rotation_matrix_y <- function(angle_degrees) {
  angle_radians <- angle_degrees * (pi / 180)
  matrix(c(cos(angle_radians), 0, sin(angle_radians),
           0, 1, 0,
           -sin(angle_radians), 0, cos(angle_radians)), 
         ncol = 3, byrow = TRUE)
}

# Function to create a rotation matrix for rotation around the Z-axis
rotation_matrix_z <- function(angle_degrees) {
  angle_radians <- angle_degrees * (pi / 180)
  matrix(c(cos(angle_radians), -sin(angle_radians), 0,
           sin(angle_radians), cos(angle_radians), 0,
           0, 0, 1), 
         ncol = 3, byrow = TRUE)
}

# Function to apply rotation to a set of 3D points
rotate_points <- function(points, angle_degrees, axis='x') {
  if(!axis %in% c('x', 'y', 'z')) stop("Axis must be 'x', 'y', or 'z'.")
  
  rotation_matrix <- switch(axis,
    'x' = rotation_matrix_x(angle_degrees),
    'y' = rotation_matrix_y(angle_degrees),
    'z' = rotation_matrix_z(angle_degrees)
  )
  
  t(rotation_matrix %*% t(points)) # Apply rotation and return new points
}

# Example usage:
points <- matrix(c(1, 0, 0,
                   0, 1, 0,
                   0, 0, 1), ncol = 3, byrow = TRUE)

# Rotate 45 degrees around the Z-axis
rotated_points <- rotate_points(points, 45, 'z')
print(rotated_points)
```

This example defines rotation matrices for the X, Y, and Z axes and provides a function to apply a rotation to a set of points. The example usage rotates a set of points (the unit vectors along each axis) 45 degrees around the Z-axis. You can modify the `angle_degrees` and `axis` to rotate around different axes and by different amounts.

### now use the result of this angle difference to determine how to rotate one vector to be aligned with a second vector

Rotating one vector to be aligned with another vector in 3D space generally involves finding the axis of rotation and the angle needed to rotate. The axis of rotation can be found by taking the cross product of the two vectors, which gives a vector perpendicular to both, serving as the axis of rotation. The angle of rotation can be determined by the method described earlier: finding the angle between the vectors.

Here's an R function that accomplishes this by first finding the angle and the axis of rotation, and then applying the rotation. The rotation itself is complex and typically involves using quaternion rotation or Rodrigues' rotation formula. For simplicity, I'll demonstrate using Rodrigues' rotation formula here:

```{r}
cross_product <- function(a, b) {
  if (length(a) != 3 || length(b) != 3) {
    stop("Both vectors must have three elements.")
  }
  
  c(a[2] * b[3] - a[3] * b[2],
    a[3] * b[1] - a[1] * b[3],
    a[1] * b[2] - a[2] * b[1])
}

# Ensuring angle_difference function is defined as per the previous instruction
angle_difference <- function(vec1, target) {
  # Calculate the dot product of the vectors
  dot_product <- sum(vec1 * target)
  
  # Calculate the magnitudes of the vectors
  mag_vec1 <- sqrt(sum(vec1^2))
  mag_target <- sqrt(sum(target^2))
  
  # Calculate the cosine of the angle between the vectors
  cos_angle <- dot_product / (mag_vec1 * mag_target)
  
  # To avoid numerical issues, ensure cos_angle is within [-1, 1]
  cos_angle <- max(-1, min(1, cos_angle))
  
  # Calculate the angle in radians and then convert to degrees
  angle_radians <- acos(cos_angle)
  
  return(angle_radians)  # Returning radians directly for rotation calculation
}

```

```{r}
# Function to rotate vec1 to be aligned with target
rotate_vector_to_align <- function(vec1, target) {
  # Calculate the cross product (axis of rotation)
  rotation_axis <- cross_product(vec1, target)
  
  # Calculate the angle between the vectors in radians
  angle_diff_rad <- angle_difference(vec1, target) * (pi / 180)
  
  # Normalize the rotation axis
  rotation_axis <- rotation_axis / sqrt(sum(rotation_axis^2))
  
  # Rodrigues' rotation formula components
  K <- matrix(c(0, -rotation_axis[3], rotation_axis[2],
                rotation_axis[3], 0, -rotation_axis[1],
                -rotation_axis[2], rotation_axis[1], 0), 
              nrow = 3, byrow = TRUE)
  I <- diag(3)
  R <- I + sin(angle_diff_rad) * K + (1 - cos(angle_diff_rad)) * (K %*% K)
  
  # Rotate vec1
  rotated_vec1 <- R %*% vec1
  
  # Return the rotated vector
  return(rotated_vec1)
}
```

```{r}
# Example usage
vec1 <- c(0, 1, 0)
target <- c(0, 1, 1)

rotated_vec1 <- rotate_vector_to_align(target, vec1)
rotated_vec2 <- rotate_vector_to_align(target, rotated_vec1)
rotated_vec3 <- rotate_vector_to_align(target, rotated_vec2)

print("Rotated Vector:")
print(rotated_vec1)
print(rotated_vec2)
print(rotated_vec3)
```

```{r}
# xyz
# Point order: L, R, Rost

R <- c(3.9203848838806152, -0.6056719422340393, -0.5852092504501343)
L <- c(3.8098082542419434, -6.479684352874756, 0.8229515552520752)
Ant <- c(-11.43181324005127, -1.661534309387207, 7.838191509246826)
names(L) <- c("x", "y", "z")
names(R) <- c("x", "y", "z")
names(Ant) <- c("x", "y", "z")

origin <- colMeans(matrix(c(L, R), ncol = 3, byrow = TRUE))

P <- cbind(c())

```

